Measuring individual differences in the understanding of gaze cues

### 2022-08-10 paper/manuscript.Rmd
add final figures

```{r setup, include = FALSE}
library("papaja")
# r_refs("r-references.bib")
```

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
```

@@

## Results
```{r splithalf}
splithalf <- readRDS(file = "../saves/gafo-splithalf.rds")
```

@@

# Supplements
## Child sample
### Webcam coding
(ref:figlab5) **Model comparison for exploratory webcam coding of parental interference**. 
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level.

```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
```

>>>>

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
theme_set(theme_classic())
```

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r sum(vali_adults$nTotal)` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_arrangedplot.png"))
```

@@

## Results
```{r splithalf}
splithalf <- readRDS(file = "../saves/gafo-splithalf-table.rds")
```

@@

# Supplements
## Child sample
### Webcam coding
(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**. 
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level.

```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
```
